Analyzing preferences differences between Chinese and English speakers in Japan hotel staying: A text mining method

### 2020-09-27 2_revisions/V0_Before submission/V0_2_First draft - After first revision by Ola/tmp-emotion_V0_1.tex
First data commit: V2-1, before second review

\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with text-mining}

%% or include affiliations in footnotes:
\author[gidai]{Elisa Claire Alemán Carreón
\corref{mycorrespondingauthor}}
\ead{elisa.claire.aleman.carreon@gmail.com}
% \orcid{0000-0002-6437-0866}

@@

\begin{abstract}

Up until recently, most studies in tourist behavior have been biased for the Western world. With the increase of Chinese outbound tourists to countries across the globe, academic interest for this group has risen. However, cross-cultural studies of their differences with other cultures are scarce and predate the current boom in the Chinese economy. This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels. Additionally, most studies choose certain factors to be analyzed in their questionnaire, and this often is limited to managerial attributes of the hotel. With the spread of the use of Web 2.0 to write online reviews of hotels, a large amount of text data is available for research purposes. With text mining, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers. This means that we can measure just how important are certain attributes of the hotel to customers, and whether those are managerial or environmental, that is, internal or external to the hotel. In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which can be used for top-weighted ranked lists with different elements and lengths. We found that Chinese customers prefer big and clean spaces and that Western customers are satisfied with friendly staff members. We also found that Chinese tourists are unsatisfied with the hotel being Chinese friendly with treatment and language and that Western customers are unsatisfied with rooms that they consider dirty, or that smell of cigarette.

\medskip
\noindent\it{Highlights}
\begin{itemize}
    \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
    \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
    \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
    \item Both customer groups have concerns about the pricing of hotels (value for money).
    \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
\end{itemize}

@@

Recently, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), with approximately a fourth of the total (25.63\%) coming from China. Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.

However, up until recently studies on social sciences, and that includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Those that do include Asian populations in their analysis, most commonly Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview-based studies with small samples, which while valid can have its limitations. This creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as "long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels. It is therefore important to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.

With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}. Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more. Data mining and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines. This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.

In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Chinese and Western English-speaking tourists populations. With this data, we can both confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past. For this purpose, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel, and perform a statistical extraction of the topics that the customers of each population are most concerned about.

@@

The objective of this study is to determine the difference in preferences between Chinese-speaking and English-speaking customers of Japanese hotels using text-mining techniques. We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure. Furthermore, we aim to measure if both customer groups have differences in priorities for the factors that are common to both groups. Furthermore, we aim to measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.

Aside from this, our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose; this means that cultural and language differences often cannot be observed in a single study.

The difference in preferences that our study uncovers can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence them to write more satisfied online reviews that will in turn increase sales and attract new customers.

@@

Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer, and as such, \cite{engel1990} states that satisfaction and dissatisfaction are therefore influenced by each customer's background. This is why Western and Asian, specifically Chinese, customers can have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the services that a hotel can provide for them, the experiences they want to have while staying at a hotel, and the level of comfort that they will have, from the moment that they choose the hotel throughout their stay. These contrasting expectations, in turn, will determine the contrasting factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
Therefore we propose our first and second hypothesis:

@@

\begin{hyp}
\label{hyp:2}
The common satisfaction and dissatisfaction factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
\end{hyp}

Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g. 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}. This leads to correlation analyses (either multivariate or single variable ones) where one factor can lead to satisfaction, while it is implied that the lack of it can lead to dissatisfaction. However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that solely correlate to satisfaction, as well as exploring factors which are solely linked to dissatisfaction. There are fewer examples of this approach, but studies have also done this in the past \cite[e.g.][]{zhou2014}. While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.

@@

% Asians vs Western behavior
In the past, tourist behavior analyzed from western samples and surveys was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}. This results in several studies focusing on only the behavior of this subset of tourists. To this day, cross-cultural studies and analyses for Asian and Western tourists have been scarce. A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; and \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.

One thing to note with the above cross-culture analyses is that they were performed before the year 2000. The current Chinese economy boom is making an increase in the influx of tourists, but the question that could be posed is whether that boom created a difference in the expectations of tourists and as such, in their satisfactions and dissatisfactions when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e. airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves.

% Universal behavior
Other more recent studies, perhaps recognizing that samples being comprised of people from Western industrialized countries aren't representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis. \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample. \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants. For another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan. In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries. The general satisfaction score was noticed to be different in those countries, but a deeper cross-cultural analysis of the satisfaction factors wasn't performed. As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.

% Western behavior 
Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data. \cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services. \cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, efficiency of check-in and check-out, restaurant and bar facilities and lobby ambiance.

% Chinese behavior
Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}. Different researchers have found that Chinese tourist populations have several specific attributes. According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities. With some overlap, \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff. Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money. According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists. And according to \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall, but the younger generations seem to do so less than their older counterparts.

% Studies are not universal.
Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire). This means that the factors will be selected through statistical methods alone. This can open opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves. In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.

@@

% Explain data mining and discovery of theory inside the data
In the current world, data is presented to us in larger and larger quantities. Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago, but they are now common for market and managerial studies, independent university students and any scientist that can connect to the Internet. Such quantities of data are available to study now more than ever, but it would be impossible for researchers to parse all of this data by themselves. As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation, and only then it can be established as knowledge. With the tools available to us in the are of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge. This process is called Knowledge Discovery in Databases.

% Text mining 
Now, there are of course many sources of numerical data to be mined, but perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form. With the introduction of Web 2.0, a never before seen quantity of valuable information is being posted to the Internet at a staggering speed. Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer, and improved on with the years. This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.

% Sentiment Analysis
More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted for decades before \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion, or even other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.

@@

In this study, we can predict that several things might occur. Our data could show satisfaction and dissatisfaction factors that are universal and it could also find strictly cultural preferences, but we expect that both of these options will present themselves. We can also assert that, if the previous literature is correct in their findings, we could arrive at very similar results, albeit using a database several orders of magnitude larger. We can also expect that, because of the lack of questionnaire design and freedom of users to record their pleasures and grievances, it is possible that we will discover patterns that were previously unnoticed by researchers.

@@

Because Chinese text doesn't have spaces, to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

@@

To apply this logic, we retrieved 50 reviews as a sample of our corpus and with the collaboration of a group of 5 Chinese students, which were split into 159 sentences. We then tagged each sentence as the classes positive or negative depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class. In the case of English reviews, we sampled 665 reviews and with the collaboration of English-speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences. Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels. This is shown in formula \ref{eq:entropy_pos}. Likewise, words with higher entropy for the dissatisfaction set than the satisfaction set by a factor of \(\alpha'\) were determined to be keywords tied to dissatisfaction in our texts. This is shown in formula \ref{eq:entropy_neg}. Examples of positive and negative sentences in English and Chinese are shown in the Appendix, in Table \ref{tab:training_examples}.

@@

In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\). However, since the lists are not necessarily of the same length, or have necessarily the same contents, and are top-weighted (where the first rank is the most important to know, with less and less importance as the ranks continue), it is necessary to use another measure of similarity. \cite{webber2010similarity} proposed a Rank-biased Overlap measurement, which takes all of these factors into consideration when calculating a value from 0 to 1, where 0 means completely different lists and 1 means the two lists are an exact match. Because our Chinese keywords (their translations, at least) don't match our English keywords one to one, it is necessary to use this method. Webber's RBO produces 3 measurements: a minimum RBO, a residual RBO (from which one can know the maximum RBO), and an extrapolated RBO (where the list is assumed to continue in the same pattern of similarity towards infinity). The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}), Where \(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists (or it could be thought as \(1-p\) being the probability to stop looking at the next item in the list), and \(X\) being the overlap between the lists. The complete process is described at length by \cite{webber2010similarity}.

@@

In order to understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the SVM classifiers. Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVM weight value. The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign. We ranked the keywords by frequency, and use their SVM weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).

We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh} (however, the latter does not have more than 7 keywords available); and for English-speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.

>>>>

\title{Analyzing preferences differences between Chinese and English speakers in Japan hotel staying: A text mining method}

%% or include affiliations in footnotes:
\author[gidai]{Elisa Claire Alemán Carreón
\corref{mycorrespondingauthor}}
\ead{s153400@stn.nagaokaut.ac.jp}
% \orcid{0000-0002-6437-0866}

@@

\begin{abstract}
Abstract

\medskip
\noindent\it{Highlights}
\begin{itemize}
    \item Chinese customers tend to prefer included breakfasts, and rooms that are big and clean.
    \item Across all hotel prices, unsatisfied Chinese customers focus on the pricing of the hotel.
    \item English speaking customers are satisfied with the staff, cleanliness, and transportation availability.
    \item English speaking customers dislike pricey hotels and have a high dislike for dirty rooms and cigarette smell.
\end{itemize}

@@

Recently, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), with approximately a fourth of the total (25.63\%) coming from China. Western countries, counting English speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.

However, up until recently studies on social sciences, and that includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Those that do include Asian populations in their analysis, most commonly Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview based studies with small samples, which while valid can have its limitations.

With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}. Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more. Data mining and big data methodologies can increase the number of samples from the hundred or so samples manageable by researchers to the hundreds of thousands that are automatically analyzed by machines. This can not only help confirm existing theories, but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.

In this study we take advantage of the availability of enormous amounts of data online for Chinese and western English speaking tourist populations' online reviews for Japanese hotels to both confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been missed in the past. For this purpose, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel, and perform a statistical extraction of the topics that the customers of each population are most concerned about.

@@

The objective of this study is to determine the difference in preferences between Chinese speaking customers and English speaking customers of Japanese Hotels using text-mining techniques. In the past, survey based studies have provided a theoretical background for specific customer groups, and cultural and language differences often cannot be observed in a single study. We propose to use large scale data from online hotel reviews in Chinese and English to study these differences in a statistical manner.

These difference in preferences can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence newer customers to write more satisfied online reviews that will in turn increase sales and attract new customers.

@@

Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer, and as such, \cite{engel1990} states that satisfaction and dissatisfaction are therefore influenced by each customer's background. This is why Western and Asian, specifically Chinese, customers can have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures. These different backgrounds will lead to different expectations of the services that a hotel can provide for them, the experiences they should have while staying at a hotel, and the level of comfort that they will have, from the moment that they choose the hotel throughout their stay. These differing expectations in turn, will determine the differing factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
Therefore we propose our first and second hypothesis:

@@

\begin{hyp}
\label{hyp:2}
Chinese and Western tourists have different priorities when it comes to similar satisfaction and dissatisfaction factors.
\end{hyp}

Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g. 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}. This leads to correlation analyses (either multivariate or single variable ones) where one factor can lead to satisfaction, while it is implied that the lack of it can lead to dissatisfaction. However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that solely correlate to satisfaction, as well as exploring factors which are solely linked to dissatisfaction. There are fewer examples of this approach, but studies have also done this in the past \cite[e.g.][]{zhou2014}. While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via sentiment classification techniques.

@@

% Asians vs Western behavior
In the past, tourist behavior analyzed from western samples and surveys was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}. This results in a number of studies focusing on only the behavior of this subset of tourists. To this day, cross-cultural studies and analyses for Asian and Western tourists have been scarce. A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to peruse the Karaoke facilities of hotels, and both groups tend to have high expectations about facilities; \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator. One thing to note with the above cross-culture analyses is that they were performed before around the year 2000. The current Chinese economy boom should make an increase in influx, but the question that could be made is if that boom created a difference in the expectations of tourists and as such, of their satisfactions and dissatisfactions when traveling.

% Universal behavior
Other more recent studies, perhaps recognizing that samples being comprised of people from Western industrialized countries isn't representative, have gone further and studied people from many countries in their samples, and performing a more universal and holistic (not cross-culture) analysis. \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample. \cite{choi2001} found that staff service quality, room quality and value for money were the top satisfaction determinants. For another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan. In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from a number of different countries; although the factors were analyzed in general without much cross-cultural analysis, although their general satisfaction score was noticed to be different. \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments and special food services.

% Western behavior 
Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data. \cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services. \cite{shanka2004} found that English speaking tourists in Perth, Australia were most satisfied with staff friendliness, efficiency of check-in and check-out, restaurant and bar facilities and lobby ambiance.

% Chinese behavior
Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}. In general Chinese tourist populations have been found to have specific attributes by different researchers. According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness and scenery in contrast to experiences and activities. With some overlap, \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan, and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness and staff. Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money. According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists. And according to \cite{gao2017chinese} who analyzed Chinese tourists and their connection to nature while traveling in different generations, Chinese tourists prefer nature overall, but the younger generations seems to do so less than their older counterparts.

% Studies are not universal.
Although the studies focusing on only Chinese tourists or only Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, the as well as the destinations, the results can vary greatly. Not only that but while there seems to be both some overlap in most studies, some factors are completely ignored in one study while not in the other.  However, with data mining, the definition of each subject or factor is left for the review writers to decide en masse, and be selected through statistical methods alone. This can open opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves. In addition, this study could help us compare the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.

@@

% Explain data mining and discovery of theory inside the data
In the current world, data is presented to us in larger and larger quantities. What was commonly only seen in very specialized large laboratories with super computers a couple of decades ago is now common data size for market and managerial studies, independent university students and any scientist that can connect to the Internet. Such quantities of data are available to study now more than ever, but it would be impossible for researchers to parse all of this data by themselves. As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining and evaluation, and only then it can be established as knowledge. With the tools available to us in the are of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge. This process is called Knowledge Discovery in Databases.

% Text mining 
Now, there are of course many sources of numerical data to be mined, but perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form. With the introduction of Web 2.0, a never before seen quantity of valuable information is being posted to the Internet at a staggering speed. Text mining then, has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer, and improved on with the years. This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.

% Sentiment Analysis
More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted since decades before \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion, or even other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.

@@

In this study, we can predict that several things might occur. Our data could show satisfaction and dissatisfaction factors that are universal and it could also find strictly cultural preferences, but we expect that both of these options will present themselves. We can also assert that, if the previous literature is correct in their findings, we could arrive to very similar results, albeit using a database several orders of magnitude larger. We can also expect that, because of the lack of questionnaire design and freedom of users to record their pleasures and grievances, it is possible that we will discover patterns that were previously unnoticed by researchers.

@@

Because Chinese text doesn't have spaces, in order to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

@@

To apply this logic, we retrieved 50 reviews as a sample of our corpus and with the collaboration of a group of 5 Chinese students, which were split into 159 sentences. We then tagged each sentence as the classes positive or negative depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class. In the case of English reviews, we sampled 665 reviews and with the collaboration of English speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences. Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels. This is shown in formula \ref{eq:entropy_pos}. Likewise, words with higher entropy for the dissatisfaction set than the satisfaction set by a factor of \(\alpha'\) were determined to be keywords tied to dissatisfaction in our texts. This is shown in formula \ref{eq:entropy_neg}. Examples of positive and negative sentences in English and Chinese are shown in the Appendix, in Table \ref{tab:training_examples}.

@@

In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\). However, since the lists are not necessarily of the same length, or have necessarily the same contents, and are top-weighted (where the first rank is the most important to know, with less and less importance as the ranks continue), it is necessary to use another measure of similarity. \cite{webber2010similarity} proposed a Rank-biased Overlap measurement, which takes all of these factors into consideration. Because our Chinese keywords (their translations, at least) don't match our English keywords one to one, it is necessary to use this method. Webber's RBO produces 3 measurements: a minimum RBO, a residual RBO (from which one can know the maximum RBO), and an extrapolated RBO (where the list is assumed to continue in the same pattern of similarity towards infinity). The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}), Where \(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists (or it could be thought as \(1-p\) being the probability to stop looking at the next item in the list), and \(X\) being the overlap between the lists. The complete process is described at length by \cite{webber2010similarity}.

@@

In order to understand the preferences of Chinese speaking tourists and English speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the SVM classifiers. In order to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy based keyword in our complete data set and their SVM weight value. The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign. We ranked the keywords by frequency, and use their SVM weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).

We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh} (however, the latter does not have more than 7 keywords available); and for English speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.
